IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/retrofit.tex
Pass on retrofit. Removed Mini-ES and clarify a bit what the embedding provides, i.e., a semantics which guarantees target language programs to be monitored

Before moving on to the formal treatment of our system, we'd like to give
a brief primer of information flow control and describe some example programs
in our system, emphasizing the parallel between their implementation
in a multi-task setting, and the traditional, ``monolithic'' programming
language feature they simulate.

Information flow control systems operate by associating data with \emph{labels},
and specifying whether or not data tagged with one label |l1| can flow
to another
label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
security policy (for example, confidential information should not flow to
a public channel), and the work of specifying the semantics of an information
flow language involves demonstrating that impermissible flows cannot happen,
a property called \emph{non-interference}.
%
In our coarse-grained floating-label approach, labels are associated with tasks.
%
The task label---we refer to the label of the currently executing task as the
\emph{current label}---serves to protect everything in the task's scope;
all data in a task shares this common label.

For our first example, here is a program which spawns a new isolated task,
and then sends it a mutable reference:
\begin{align*}
    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
    & |in TI (send (IT i) l (IT (ref true)))|
\end{align*}
For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
message, and then \textbf{send}s the task a mutable reference |(ref
true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
could be used to violate information flow control if the tasks had differing labels.

While simple, this example demonstrates some of our general design principles.  When these
constructs are treated as isolated tasks, each of which have their own heaps, it
is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  From
there, we can further ask: given the obviously safe formulation with
separate heaps, can this fact be useful for showing the safety of a
semantics which only has a single heap? (We answer this question
positively in Section~\ref{sec:single-heap}.)  Finally, this na\"ive
semantics violates expectations about how inter-task communication works
on a shared heap and strongly suggests one should restrict the types of
data which may be passed between tasks (for example, in JavaScript, one
might only allow JSON objects to be passed between tasks, rather than
general object structures).

Here are two more examples of language features which have an
interesting interpretation when viewed in the setting of multiple tasks.

\paragraph{Stack frames versus scheduling}  One feature which is
supported by some information flow control systems is the ability to
temporarily raise the current label in order to do computation on data
(as done by LIO's |toLabeled| and Breeze's
brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
achieve termination-insensitive non-interference: if the high secrecy
section doesn't terminate, this is observable by the non-execution of
the defunct public continuation.

\begin{figure}
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId in| \\
%%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
\caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
\end{figure}

When considering tasks, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a new
isolated task; a sample encoding using our language is shown in
Figure~\ref{fig:toLabeled}.
However, this is not enough: in a stack discipline, one generally
expects stack entries to be processed in order, rather than in parallel
as would be suggested by isolated tasks.  The sequential processing of
the task queue corresponds to a specific \emph{scheduling policy} of
these tasks.  The recasting of the problem to one of scheduling
highlights the essential difference between termination-insensitive and
termination-sensitive non-interference, and we will show how different
scheduling policies give different security guarantees.

\paragraph{Exceptions versus message passing}
Another language feature that has caused difficulty for
many information flow control systems is exceptions handling,
when built on top of this stack discipline.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation; hence, one must
explicitly ensure that |toLabeled| does not propagate exceptions.

When stack frames are treated as isolated tasks, the correct semantics
are achieved automatically.
%
Exceptions simply stop when the hit the top-level of a task:
the only way for the frame to communicate information is by
initiating inter-task message passing.
%
For instance, 
\begin{code}
TI(toLabeled l (IT (if te then fail else true))); true
\end{code}
always evaluates to |true|, regardless of the value of |te|.

\subsection{Preliminaries}

Our goal now is to
describe how to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for SWAPI.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without having too much detail (and because the embedding really
doesn't care about what, exactly, is in the target language); we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

\subsection{Target Language: Mini-ES}

In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
mutable references and fixpoint, prepared for combination with an
information flow control language.  The presentation is mostly standard, and utilizes Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
operational semantics of the system.  One peculiarity is that our language
defines an evaluation context |tE|, but, the evaluation rules have been
expressed in terms of a different evaluation context |curlyRedE|;
Here, we follow the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining
semantics of multiple languages. 
To derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
However, when we combine this language with an IFC language, we
reinterpret the meaning of this evaluation context.

In general, we require that a target language be expressed in terms
of some global machine state |tS|, some evaluation context |tE|,
some expressions |te|, some set of values |tv| and a \emph{deterministic}
reduction relation on full configurations $|tS| \times |tE| \times |te|$.

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te
       | ref te | !te | te := te | fix te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE | fix tE

te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
let tx = te1 in te2  @= (\tx.te2) te1
\end{code}

\inferrule[T-app]
{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}

\and
\inferrule[T-ref]
{ | fresh ta | }
{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

\and
\inferrule[T-deref]
{ |memberf ((ta, tv)) tS| }
{| conf tS (!ta) -> conf tS (tv) |}

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}

\and
\inferrule[T-fix]
{ }
{| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}

%\and
%\inferrule[T-fail]
%{ }
%{| conf tS ( tE [ fail ] ) -> conf tS fail |}
\end{mathpar}

\caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
mutable references and general recursion. |FV(te)| returns the set of free
variables in expression |te|.}
\label{fig:ml}
\end{figure}

@@

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|).
    \item Operations for inspecting (\textbf{getLabel}) and modifying
    (\textbf{setLabel}) the current label of the task (a task can only increase its label).
    \item Operations for non-blocking inter-task communication (\textbf{send}
    and \textbf{recv}), which interact with the global store of per-task
    message queues |iS|.
%%     Labels are associated with message at the time of
%%     the send; the label on a message must always be at least as sensitive as that
%%     of the sending thread, since, conceptually, once a message is put on a
%%     message queue it is no longer protected by the current label, rather it is
%%     protected by the message label.
%%     Dually, when reading a message with |recv| the current label of the
%%     receiver must be at least as high as the message label.
    \item A sandboxing operation used to spawn new isolated tasks. In
    concurrent settings |fork| corresponds to a fork-like primitive,
    whereas in a
    sequential setting, it more closely resembles the LIO
    |toLabeled|~\cite{lio} and Breeze
    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.
\end{itemize}

@@

\subsection{The Embedding}
Figure~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

The \textsc{I-sandbox} rule is used to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of |klone|, but all our
security claims will hold regardless of the choice of |klone|.

@@

%
As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
\textsc{I-border} define the syntactic boundaries between the IFC and target
languages.
%
Intuitively, the boundaries respectively correspond to an upcall into and
downcall from the IFC runtime.
%
As an example, taking |targetLangML| as the target language, we can now define a
blocking receive (inefficiently) in terms of the asynchronous |recv| as series
of cross-language calls:
\begin{code}
  brecvf ix1 ix2 ie @=
  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
\end{code}

We note that our embedding corresponds to the lump embedding
of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
treated opaquely in the other.
%
Indeed since our embedding is defined for an arbitrary language |targetLang|,
we cannot do better.
%
However, when we have more information about the target language, it is
possible to add rules for a natural embedding of expressions that occur in both
languages.  In our specific example with |targetLangML|, we can choose to
preserve booleans across language boundaries as follows:
\begin{mathpar}
\inferrule
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}

For any target language |targetLang| and scheduling policy |alpha|, this
embedding defines an IFC language, which we will
refer to as |specLang alpha targetLang|.

>>>>

%% Before moving on to the formal treatment of our system, we'd like to give
%% a brief primer of information flow control and describe some example programs
%% in our system, emphasizing the parallel between their implementation
%% in a multi-task setting, and the traditional, ``monolithic'' programming
%% language feature they simulate.

%% Information flow control systems operate by associating data with \emph{labels},
%% and specifying whether or not data tagged with one label |l1| can flow
%% to another
%% label |l2| (written as |canFlowTo2 l1 l2|).  These labels encode the desired
%% security policy (for example, confidential information should not flow to
%% a public channel), and the work of specifying the semantics of an information
%% flow language involves demonstrating that impermissible flows cannot happen,
%% a property called \emph{non-interference}.
%% %
%% In our coarse-grained floating-label approach, labels are associated with tasks.
%% %
%% The task label---we refer to the label of the currently executing task as the
%% \emph{current label}---serves to protect everything in the task's scope;
%% all data in a task shares this common label.

%% For our first example, here is a program which spawns a new isolated task,
%% and then sends it a mutable reference:
%% \begin{align*}
%%     & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
%%     & |in TI (send (IT i) l (IT (ref true)))|
%% \end{align*}
%% For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
%% |sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
%% message, and then \textbf{send}s the task a mutable reference |(ref
%% true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
%% could be used to violate information flow control if the tasks had differing labels.  At this point, the designer of an IFC system might add label checks to mutable references, to check the labels of the reader and writer---solving the leak, but also dooming the performance of mutable references in the system.

%% Our design principles suggests a different resolution: when these
%% constructs are treated as isolated tasks, each of which have their own heaps, it
%% is obviously the case that there is no sharing: in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
%% not be shared, the two systems are morally equivalent. (We elaborate on
%% this formally in Section~\ref{sec:single-heap}.)  Finally, these
%% semantics strongly suggest that one should restrict the types of
%% data which may be passed between tasks (for example, in JavaScript, one
%% might only allow JSON objects to be passed between tasks, rather than
%% general object structures).

%% Here are two more examples of language features which have an
%% interesting interpretation when interpreted as task communication.

%% \paragraph{Stack frames versus scheduling}  One feature which is
%% supported by some information flow control systems is the ability to
%% temporarily raise the current label in order to do computation on data
%% (as done by LIO's |toLabeled| and Breeze's
%% brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
%% stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
%% enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
%% the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
%% achieve termination-insensitive non-interference: if the high secrecy
%% section doesn't terminate, this is observable by the non-execution of
%% the defunct public continuation.

%% \begin{figure}
%% \begin{align*}
%%     & |toLabeled l te @= | \\
%%     & |tab let i = taskId in| \\
%% %%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
%%     & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
%%     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
%% \end{align*}
%% \caption{Encoding of toLabeled using isolated tasks.}\label{fig:toLabeled}
%% \end{figure}

%% When considering tasks, we will instead say that the allocation of a new
%% stack frame with a raised label corresponds to the creation of a new
%% isolated task; a sample encoding using our language is shown in
%% Figure~\ref{fig:toLabeled}.
%% There is one more ingredient: in a stack discipline, one generally
%% expects stack entries to be processed in order, rather than in parallel
%% as would be suggested by isolated tasks.  The sequential processing of
%% the task queue corresponds to a specific \emph{scheduling policy} of
%% these tasks.  In fact, the choice of scheduling here is the essential difference that
%% determines whether or not one can prove termination-insensitive or
%% termination-sensitive non-interference. We will show how different
%% scheduling policies give different security guarantees.

%% \paragraph{Exceptions versus message passing}
%% Another language feature that has caused difficulty for
%% many information flow control systems is exception handling
%% when built on top of this stack discipline.
%% %
%% The key difficulty appears when considering the propagation of exceptions
%% across stack boundaries where the current label is restored.
%% %
%% If the exception crosses this boundary, it can leak information about the
%% inner secret computation into a public computation; hence, one must
%% explicitly ensure that |toLabeled| does not propagate exceptions.
%% %
%% When stack frames are treated as isolated tasks, the correct semantics
%% are achieved automatically.
%% %
%% Exceptions simply stop when the hit the top-level of a task:
%% the only way for the frame to communicate information is by
%% initiating inter-task message passing.
%% %
%% For instance,
%% \begin{code}
%% TI(toLabeled l (IT (if te then fail else true))); true
%% \end{code}
%% always evaluates to |true|, regardless of the value of |te|.

%\subsection{Preliminaries}

Our goal now is to describe how to take a \textbf{{\color{red} target
language}}
%with a formal operational semantics
and combine it with an \textit{{\color{blue} information flow control language}}
(or IFC-aware API).  It is precisely this combination what enables executing the
target language under a coarse-grained IFC monitor. In Section~\ref{sec:real},
we show that taking ECMAScript as the target language and combining it with our
IFC language provides the formal semantics for COWL~\cite{swapi}.  In this
section, we intentionally avoid too much detail about the target language; after
all, our technique really does not care too much about what, exactly, is in
there.
% we discuss the proper
% embedding in more detail in Section~\ref{sec:real}.

%use a simple,
%untyped lambda calculus with mutable references and fixpoint in place of
%ECMAScript,
%to demonstrate some of the key properties without having too much
%detail

@@

\subsection{Target Language}

%% In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
%% mutable references and fixpoint, prepared for combination with an
%% information flow control language.
The framework assumes target languages utilizing
%The presentation is mostly standard, and utilizes
Felleisen-Hieb reduction semantics~\cite{Felleisen:1992:RRS:136293.136297} in
order to define their operational semantics. Specifically, we require that a
target language be expressed in terms of some global machine state |tS|, some
evaluation context |tE|, some expressions |te|, some set of values |tv| and a
\emph{deterministic} reduction relation on full configurations $|tS| \times |tE|
\times |te|$.

One peculiarity of our approach is that reductions rules in the target language
are reformulated in terms of a different evaluation context |curlyRedE| (instead
of |tE|); Here,
we follow the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} in order to simplify combining
semantics of multiple languages. To derive the usual operational semantics for
the target language, the evaluation context merely needs to be defined as |conf
tS te @= tS, bracket tE te|.  However, when we combine this language with an IFC
language, we reinterpret the meaning of |conf tS te|.

%% \begin{figure}
%% \begin{code}
%% tv   ::= \tx.te | true | false | ta
%% te   ::= tv | tx | te te | if te then te else te
%%        | ref te | !te | te := te | fix te
%% tE   ::= tHole | tE te | tv tE | if tE then te else te
%%        | ref tE | !tE | tE := te | tv := tE | fix tE

%% te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
%% let tx = te1 in te2  @= (\tx.te2) te1
%% \end{code}

%% \begin{mathpar}

%% \inferrule[T-app]
%% { } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}

%% \and
%% \inferrule[T-ifTrue]
%% { } {| conf tS (if true then te1 else te2) -> conf tS te1|}

%% \and
%% \inferrule[T-ifFalse]
%% { } {| conf tS (if false then te1 else te2) -> conf tS te2|}

%% \and
%% \inferrule[T-ref]
%% { | fresh ta | }
%% {| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

%% \and
%% \inferrule[T-deref]
%% { |memberf ((ta, tv)) tS| }
%% {| conf tS (!ta) -> conf tS (tv) |}

%% \and
%% \inferrule[T-ass]
%% { }
%% {| conf tS (ta := tv) -> conf (bracket tS (mapsto ta tv)) tv |}

%% \and
%% \inferrule[T-fix]
%% { }
%% {| conf tS (fix (\ x . e)) -> conf tS ({fix (\ x . e)/x} e) |}

%% %\and
%% %\inferrule[T-fail]
%% %{ }
%% %{| conf tS ( tE [ fail ] ) -> conf tS fail |}
%% \end{mathpar}

%% \caption{|targetLangML|: simple untyped lambda calculus extended with booleans,
%% mutable references and general recursion. |FV(te)| returns the set of free
%% variables in expression |te|.}
%% \label{fig:ml}
%% \end{figure}

@@

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|).
    \item Operations for inspecting (\textbf{getLabel}) and modifying
    (\textbf{setLabel}) the current label of the task (a task can only increase its label).
    \item Operations for non-blocking inter-task communication (\textbf{send}
    and \textbf{recv}), which interact with the global store of per-task
    message queues |iS|.
%%     Labels are associated with message at the time of
%%     the send; the label on a message must always be at least as sensitive as that
%%     of the sending thread, since, conceptually, once a message is put on a
%%     message queue it is no longer protected by the current label, rather it is
%%     protected by the message label.
%%     Dually, when reading a message with |recv| the current label of the
%%     receiver must be at least as high as the message label.
    \item A sandboxing operation used to spawn new isolated tasks. In concurrent
      settings |fork| corresponds to a fork-like primitive, whereas in a
      sequential setting, it more closely resembles a sub-computation which might
      temporarily raise the floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.
\end{itemize}

@@

\subsection{Monitored executions}
Figure~\ref{fig:embedding} provides all of the rules responsible for % actually
carrying out the embedding of the IFC language with the target language. The
resulting semantics then guarantees that programs written in the target language are
monitored. The most important feature of this embedding is that every task
maintains its own copy of the target language global state and evaluation
context, thus enforcing isolation between various tasks.  In more detail:

@@

The \textsc{I-sandbox} rule is used to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a the function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove certain entries from the state.
\Red{Ale: TODO we need to say that what is important about k is that there is no
sharing between tasks. Moreover, |klone| should be implementable either by the
target language or its runtime system}
% ---we will discuss   In Section~\ref{sec:concrete}, we give a more detailed
% discussion of the implications of the choice of |klone|, but all our
% security claims will hold regardless of the choice of |klone|.

@@

%
As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
\textsc{I-border} define the syntactic boundaries between the IFC and target
languages.
%
Intuitively, the boundaries respectively correspond to an upcall into and
downcall from the IFC runtime.
%
%% As an example, taking |targetLangML| as the target language, we can now define a
%% blocking receive (inefficiently) in terms of the asynchronous |recv| as series
%% of cross-language calls:
%% \begin{code}
%%   brecvf ix1 ix2 ie @=
%%   tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
%% \end{code}

%% We note that our embedding corresponds to the lump embedding
%% of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
%% treated opaquely in the other.
%% %
%% Indeed since our embedding is defined for an arbitrary language |targetLang|,
%% we cannot do better.
%% %
%% However, when we have more information about the target language, it is
%% possible to add rules for a natural embedding of expressions that occur in both
%% languages.  In our specific example with |targetLangML|, we can choose to
%% preserve booleans across language boundaries as follows:
%% \begin{mathpar}
%% \inferrule
%% { |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
%% \and
%% \inferrule
%% { |b member {true, false}| } {| intE (TI b) -> intE b |}
%% \end{mathpar}

For any target language |targetLang| and scheduling policy |alpha|, this
embedding defines a coarse-grained IFC-aware language, which we will
refer to as |specLang alpha targetLang|.
